---
title: "Ideas"
author: "Lucy, Alex, Jacob, Wills"
date: "11/5/2019"
output: html_document
keep_md: yes
---
```{r,echo=TRUE,include=FALSE}
library(mosaicData) 
library(lubridate)
library(ggthemes)
library(tidyverse)
library(plotly)
library(readr)
```

# Link to slack because we need some form of communication

https://join.slack.com/t/data-science-gang/shared_invite/enQtODEzMDY5MzY4OTMxLTdmMzlhZGFiNmJlYjNmZTg2ODI1MDZhM2UyNjUzMDRlOTU1MDVjZTBlZjBhNTc1YTFjN2U5MTE2ODc0MTc4YzM

Powerlifting Data
  Analyze max increases based on weight/gender

MMA Data
  Analyze weight class head to head
  Do differences in weight change how victorious a person is?

NCAA BBall Data
  Do teams with more of certain type of player group (height, ethnicity) win more?
  
College
  Analyze salaries by major/school location
  https://www.kaggle.com/wsj/college-salaries 
 
```{r}
degrees_that_pay_back <- read_csv("degrees-that-pay-back.csv")
salaries_by_college_type <- read_csv("salaries-by-college-type.csv")
salaries_by_region <- read_csv("salaries-by-region.csv")

view(degrees_that_pay_back)
view(salaries_by_college_type)
view(salaries_by_region)
```
```{r}
#Creates variable start_med_sal which is the starting median salary without $ and , so it can be computed as a numerical variable
salaries_by_region$start_med_sal = as.numeric(gsub("[\\$,]", "", salaries_by_region$`Starting Median Salary`))

Shoulda_gone_to_California <- salaries_by_region %>% 
  ggplot() +
  geom_boxplot(aes(x=Region,y=start_med_sal)) +
  theme_minimal() +
  labs(title="Starting Median Salary by Region",
       y="Starting Median Salary")

ggplotly(Shoulda_gone_to_California)
```
 - Looks like we made the wrong choice 
 
```{r}
#did it again
salaries_by_college_type$start_med_sal = as.numeric(gsub("[\\$,]", "", salaries_by_college_type$`Starting Median Salary`))

Atleast_we_arent_a_state_school <- salaries_by_college_type %>% 
  ggplot() +
  geom_boxplot(aes(x=`School Type`,y=start_med_sal)) + 
  theme_minimal() +
  labs(title="Starting Median Salary by School Type",
       y="Starting Median Salary")

ggplotly(Atleast_we_arent_a_state_school)
```
 - Starting to question my life choices
 
 
  